Investigating the Effect of Dataset Representivity for Image Colourisation

### 2019-10-07 Paper/paper.tex
Updated introduction

Therefore, the aim is to investigate what percentage of the training dataset has to be of local origin compared to the international origin of the remainder of the dataset. However, constructing and testing datasets to determine such a goal is both time consuming and expensive in terms of financial and computational resources required. Hence, the approach of image colourisation has been selected as it allows an uncomplicated procedure of collecting publicly-available images, thus providing a simple way to build a diverse dataset which does not need to be labelled or require excessive computational time since the machine learning approach required is one of supervised learning where the expected outcome is derived from the images themselves.

>>>>

Therefore, the aim is to investigate what percentage of the training dataset has to be of local origin compared to the international origin of the remainder of the dataset. However, constructing and testing datasets to determine such a goal is both time consuming and expensive in terms of financial and computational resources required. Hence, the approach of image colourisation has been selected as it allows an uncomplicated procedure of collecting publicly-available images of both International and South African settings, thus providing a simple way to build a diverse dataset which does not need to be labelled or require excessive computational time since the machine learning approach required is one of supervised learning where the expected outcome is derived from the images themselves.
